

\documentclass[letterpaper, 12pt]{article}

%
% General Notes
%

% Only use T1 fonts as these allow scaling via cm
% \usefont encoding family series shape size
% encoding
%	T1
%family
%	lmr
%	cmr
%	phv
%series
%	m - medium
%	b - bold 
%shape 
%	n - normal upright
%	it - italic
%	sl - slanted
%	sc - small caps


% Change the numerals used in enumerate
% \renewcommand{\labelenumi}{\Roman{enumi}.}


%
% variables
%

\newcommand{\vtitle}{Wallflowers}
\newcommand{\vauthor}{wandyezj}
\newcommand{\vversion}{2026-04-25}

% symbol - to read out loud
\newcommand{\vreadsymbol}{$\triangleright$}

% symbol - is an example
\newcommand{\vsymbolexample}{$\in$}

% symbol - is a ref link to a section
\newcommand{\vsymbolref}{$\cdots$}


% Fonts

% options
% cmssq
% pag
% phv .35cm
% lmr

% font - default
\newcommand{\vfontdefault}{cmssq}
\newcommand{\vfontdefaultsize}{0.4cm}

% font - read
\newcommand{\vfontread}{lmr}
\newcommand{\vfontreadsize}{0.4cm}

%
% Links
%

% Specific Links
\newcommand{\vlinkrefsectionpartynarrate}{section:partynarrate}
\newcommand{\vlinkrefsectionpartyimpression}{section:partyimpression}

\newcommand{\vlinkrefsectionpartynormalround}{section:partynormalround}
\newcommand{\vlinkrefsectionpartybloom}{section:partybloom}

\newcommand{\vlinkrefsectionpartyturn}{section:partyturn}

% \clinkref
% Create a reference for a link
\newcommand{\clinkref}[1]{\label{#1}}

% \clink
% Create a link
\newcommand{\clink}[1]{\hyperref[#1]{\vsymbolref}}



%
% Q & A
%

\newcommand{\cquestion}[1]{\subsection{#1}}

%
% Commands
% 


% \ccard
% Denote a index card with text on it
\newcommand{\ccard}[1] {
	\begin{tikzpicture}
		\node[draw,align=center,inner sep=0.5cm,minimum width=4.5cm] at (3,0) {#1};
	\end{tikzpicture}
}

%italic
\newcommand{\ci}[1]{\textit{#1}}

\newcommand{\csetfontsize}[1]{
	\fontsize{#1}{#1}
	\selectfont
}

\newcommand{\csetfont}[1]{
	\usefont{T1}{#1}{m}{n}
	\selectfont
}

% read commands are to format to indicate it should be read out loud
\newcommand{\csetfontread}{
	\usefont{T1}{\vfontread}{m}{n}
	\csetfontsize{\vfontreadsize}
	%\linespread{2}
	\selectfont
	\setlength{\parskip}{2mm} % Custom spacing
	\setlength{\parindent}{0pt}
}

% \cnot
% Denote - NOT
\newcommand{\cnot} {\emph{NOT} }

% \cread 
% Denote - this is something that should be read out loud
\newcommand{\cread}[1]{
		%\fbox{
			%\texttt{
{\csetfontread \vreadsymbol #1}
			%}
		%}
}

\newenvironment{eboxed}
{\begin{center}
		\begin{tabular}{|p{0.95\textwidth}|}
			\hline\\
		}
		{ 
			\\\\\hline
		\end{tabular} 
	\end{center}
}

% Denote this is something to be read out loud
\newenvironment{eread}
{
	%\begin{quote}
		
		%\begin{eboxed}
			\csetfontread
			\setlength{\parindent}{0pt}
			\vreadsymbol \linebreak
		}
		{
		%\end{eboxed}
%\end{quote}
}


%
% Packages
%



% Fonts
%\input Zallman.fd %\newcommand*\initfamily{\usefont{U}{Zallman}{xl}{n}}


%\usepackage{almendra}
%\usepackage{lmodern} 
%\usepackage[T1]{fontenc}
% Scalable Font Sizes
%\usepackage{lmodern} 
%\usepackage{type1cm}
%\usepackage[T1]{fontenc}

% Other Packages
\usepackage{geometry}


%\geometry{a4paper, margin=1in}

\geometry{
	paperwidth=4.375in,
	paperheight=8.75in,
	margin=0.25in,
	bottom=0.5in
	}

% Control margines of enums with parameters
\usepackage{enumitem}

% font 12 pt


% Drawings
\usepackage{tikz}

% Paragraphs
\usepackage{parskip}
% Framing
%\usepackage{framed}
%\usepackage{mdframed}


%\usepackage{anyfontsize}
%\usepackage{scrextend}
%\changefontsizes{18pt}

% Clickable Links
\usepackage{hyperref}

%
% Setup
%



\title{\vtitle}
\author{\vauthor}
\date{}


%
% Macro Sections
%

\newcommand{\cpagetitle}{
\begin{titlepage}
	\centering
	\vspace*{4cm}
	{
		\csetfontsize{1.8cm}
		\usefont{OT1}{pag}{x}{n}
		\vtitle
	}
	\vspace*{0.5cm}
	
	{\large by \vauthor}
	\vspace*{0.5cm}
	\linebreak
	{\small \vversion }
	
	\vspace*{\fill}
\end{titlepage}
\pagebreak
}



%\renewcommand{\familydefault}{cmssq}
\begin{document}
{
% Global Font Control
\csetfont{\vfontdefault}
\csetfontsize{\vfontdefaultsize}
\raggedright

% Global Section Control
% Remove numbers from subsections
\setcounter{secnumdepth}{1}

%
% Title Page
%

\cpagetitle


%
% Section Start
% Materials
%

\section{What you need to play}

\begin{itemize}
	\item Three or four players
	\item Blank Index cards
	\item Pens or pencils
	\item (optional) Token to track whose turn it is.
\end{itemize}



%
% Section Start
% Introduction
%

\pagebreak
\section{Introduction}

Read the following aloud:

\begin{eread}
We are playing wallflowers at a large party.

Your wallflower showed up to the party by themselves, and is now watching the party alone from the sidelines.

Initially, you know nothing about your wallflower except their alias.

What does your wallflower see, think, and feel - as they watch the party unfold?

Do they want to join the party or leave?

Don't try to answer yet!

You will discover everything about your wallflower through play.
\end{eread}

\pagebreak
\section{Alias}


Read the following aloud:


\begin{eread}
Each player will play one wallflower.

Pick an alias for your wallflower named after a flower.

Each alias must be a single word flower name and start with a different letter.

Pick from the list below or create your own:

\end{eread}

\begin{verbatim}
Azalea
Begonia
Camellia
Dahlia
Erysimum
Foxglove
Goldenrod
Hyacinth
Indigo
Jasmine
Kudzu
Lotus
Marigold
Nerine
Orchid
Poppy
Quince
Rose
Sage
Tulip
Ulmus
Violet
Willow
Xanthium
Yarrow
Zenobia
\end{verbatim}

\pagebreak
\section{Place Cards}

Create place cards to help everyone keep track of who is playing each wallflower.
\linebreak
\linebreak
Have each player write down their name and their \linebreak wallflower's alias on a folded index card and place it in front of them.

\begin{enumerate}

\item Give each player an index card and a pen.
\item \cread{Fold your index card in half to make a tent.}
\item \cread{Write down your \textit{wallflower alias} and your name on both sides.}

Example

%\ccard{Wallflower Alias\\ \\ (Player Name)}

\ccard{Azalea\\ \\ (Ace)}

\item \cread{Place the card in front of you so everyone can see.}

\end{enumerate}

\pagebreak
\section{Wallflower Deck}

Create the wallflower deck.

\begin{enumerate}
	\item Give each player a blank index card. 
	
	\item \cread{Write down your wallflower alias on one side - leaving the back blank.} 
	
	Example
	
	%\ccard{\\Wallflower Alias\\} 
	
	\ccard{\\Azalea\\}


	
	\item Collect these index cards.
	
\end{enumerate}

\pagebreak
\section{Setting}

What type of party are we playing?


\begin{enumerate}
	\item Pick an age group for everyone at the party:
		\begin{itemize}
			\item High School
			\item College
		\end{itemize}
	\item Pick a setting:
		\begin{itemize}
			\item House party at a wealthy house
			\item Kegger in the woods
			\item Bonfire on the beach
		\end{itemize}
	

\end{enumerate}

\pagebreak
\section{Attendees}

Who shows up to the party?

We will each create one character our wallflowers  see at the party.

In any order: Describe this character. What do they look like? What are they wearing?

\pagebreak



\section{Party}

\subsection{Overview}
The party takes place across five rounds. Each round, every player takes one turn.

\vspace{0.4cm}
The first four rounds: \clink{\vlinkrefsectionpartynormalround}
\vspace{0.4cm}
\linebreak
On your turn, narrate something at the party \ci{all} wallflowers notice. Then, another player will reveal their wallflower's impression.

Each round, every player will narrate once, and reveal their wallflower's impression once.

\vspace{0.4cm}
The final bloom round: \clink{\vlinkrefsectionpartybloom} 
\vspace{0.4cm}
\linebreak
All wallflowers will bloom - joining or leaving the party.


\pagebreak
\subsection{Normal Round} \clinkref{\vlinkrefsectionpartynormalround}


\subsubsection{At the beginning of each round}

\begin{enumerate}
	\item Collect the wallflower cards and shuffle the wallflower deck.
	\item Rotate the opening player clockwise. This way, in a four player game, everyone opens the round once.
	\item The opening player reads the opening line for the round and narrates first.
	\item Turns proceed clockwise.
	
	
\end{enumerate}

\subsubsection{Round Opening Lines}

\begin{enumerate}
	\renewcommand{\labelenumi}{\Roman{enumi}.}
	\item It's early in the evening, not many people are here yet.
	
	\item It's still early in the evening, people are arriving and socializing.
	
	\item It's the middle of the night, the party is packed, the music is up.
	
	\item It's still the middle of the night, the music and energy have shifted to be more relaxed.
\end{enumerate}

\pagebreak
\subsubsection{On Your Turn}
On your turn:

\begin{enumerate}[leftmargin=*]
	\item Narrate \clink{\vlinkrefsectionpartynarrate}
	\item Read
		\begin{itemize}
			\item \cread{Our wallflowers all saw this. What is your wallflowers impression? What are they thinking? What are they feeling?}
		\end{itemize}
		
	\item Pause
		\begin{itemize}
			\item Everyone think in silence about your wallflower's impression. Hold up your hand when you are ready.
			\item Think about your own wallflower's impression.
		\end{itemize}
	
	\item Draw
		\begin{itemize}
			\item Select a wallflower to reveal their thoughts.
			\item The player who narrates should always be different from the player revealing their wallflower's impression.
			\item Draw from the wallflower deck:
			\begin{itemize}
				\item If you are the second to last player, check the deck to make sure the final player does not draw their own card.
				\item If you draw your own card, set it aside, draw again, then shuffle your own card back in.
				\item If you are the last player and draw your own card - Oops! Narrate your own wallflower's impression.
			\end{itemize}
			\item Hand the player their wallflower card, remove it from the deck for the rest of the round. Each wallflower reacts only once per round.
		\end{itemize}

\item Impression \clink{\vlinkrefsectionpartyimpression}
	\begin{itemize}
		\item Have the player who controls the drawn wallflower reveal their wallflower's impression.
	\end{itemize}

\end{enumerate}


\pagebreak
\subsubsection{Narrate} \clinkref{\vlinkrefsectionpartynarrate}
Describe something at the party all wallflowers notice. This might be an object, person, scene, or detail.

\vspace{2mm}

In Round:

\begin{enumerate}
	\renewcommand{\labelenumi}{\Roman{enumi}.}
	
	\item Introduce something new.
	\item Introduce something new or build on something another player has introduced.
	\item Build on something another player has introduced.
	\item Build on something another player has introduced.
\end{enumerate}

\vspace{5mm}
Only describe what the wallflower's can directly observe.

\begin{itemize}
\item Do \cnot use judgement words.
\item Do \cnot describe interaction with a wallflower.
\item Do \cnot describe what a wallflower might know, think, or feel.
\end{itemize}

\vspace{5mm}
Examples

\begin{itemize}
\renewcommand{\labelitemi}{\vsymbolexample}

\item A buff guy with a huge smile on his face walks past. He's wearing a baseball cap with the high school Griffin mascot, a T-Shirt with that says "Rock Punks" in gigantic pink letters, and shorts paired with socks and sandals - showing off incredibly smooth legs.

\item A group of guys from the football team, squashed together on the white couch, are staring at the TV, and suddenly jump up cheering - a bowl of popcorn tumbles onto the floor, flinging popcorn everywhere.

\item A girl tightly gripping a boys hand drags him to the front door. Her brows are furrowed and tears wet her cheeks.

\item A group of girls from the cheer squad dressed in matching hoodies and sweat pants are in a circle in the corner laughing so loudly you can hear it across the room.


\end{itemize}

\pagebreak
\subsubsection{Impression} \clinkref{\vlinkrefsectionpartyimpression}

Narrate your wallflower's impression in the 3rd person.

Describe what your wallflower pays attention to. What do they think? How do they feel about what they observed?

Based on your wallflower's reaction do they want to join or leave the party?

Only describe what your wallflower is thinking or feeling.

\begin{itemize}
	\item Your wallflower may \emph{NOT} take action.
	\item Your wallflower may \emph{NOT} join or leave the party.
\end{itemize}

\vspace{5mm}
Example:
\begin{itemize}
\renewcommand{\labelitemi}{\vsymbolexample}
\item
\begin{quote}
We see Azalea alone. 

Azalea sees... the cheer squad laughing in the corner. Must be nice to fit in, and feels awkward.

Azalea wants to... join the party.
\end{quote}
\end{itemize}


\pagebreak
\subsection{Bloom} \clinkref{\vlinkrefsectionpartybloom}

This is the final round.

Read the following aloud:

\begin{eread} 
It's late, the party is starting to wind down, some people are starting to leave, others are settling into quieter conversations.

Does your wallflower join or leave the party?

\end{eread}

\subsubsection{Turn Order}

Have one player:

\begin{enumerate}
	\item Shuffle the wallflower deck.
	\item Draw from the wallflower deck and have each wallflower go as they are called.
\end{enumerate}

\subsubsection{On your turn}

\begin{enumerate}
	\item Ask the other players if your wallflower joins or leaves the party. Why?
	\item Decide if your wallflower joins or leaves the party.
	\item Narrate a short vignette of your wallflower joining or leaving the party. 
	\begin{itemize}
		\item Why did they stop being a wallflower?
		\item What is your wallflowers feeling?
	\end{itemize}

	
\end{enumerate}


\pagebreak
\section{Q \& A}



\cquestion{What changes for online play?}

For online play you will need:

\begin{itemize}
	\item A video chat client so everyone can see and hear each other.
	\item A shared document everyone can view and edit.
\end{itemize}


In the shared document, list each wallflower alias and player name in a section titled 'Wallflowers'.

Example:

\begin{verbatim}
Wallflowers

- Azalea (Ace)
- Begonia (Ben)
- Camellia (Cal)
- Dahlia (Dan)
\end{verbatim}


Clockwise is considered down.

After the last player in the list - loop back the the top.

The facilitator will create the deck of cards, they will shuffle and draw for everyone as required.


\cquestion{Can we play with other party contexts?}

Yes. However you will need to discuss and agree on that shared context with other players.

Examples

\begin{itemize}
	\item Corporate Party
\end{itemize}


\cquestion{Can wallflowers observe each other?}

No. Wallflowers are isolated and don't notice each other.

Reason: This would contradict the design goal of the wallflowers observations revealing themselves.


\cquestion{Why narrate from the 3rd person?}

I think it helps player more safely explore their wallflower.

Narrating in the 1st person often increases the risk of character bleed.

\cquestion{Why rotate which player starts each round?}

I want different players to take turns reading the rounds starting line.

The first description of what is happening at the party can have a lot of influence on the rest of the round. I want to get different players' ideas.

Additionally, this balances the draw probability of the wallflower deck.


\cquestion{Why randomize wallflower impressions?}

Wallflowers don't get to choose what they see.

I want players to stay engaged - there is a possibility their wallflower will be called on.

I want different players to have a chance to respond to other players narration.

\cquestion{Why hide which wallflower has an impression from the narrator?}

The party action is explicitly separate from the wallflowers.

The wallflowers are on the sidelines, they should not be considered in a players narration of party events.

I want the player doing narration to be free to narrate what happens at the party.

\pagebreak
\cquestion{Why have every wallflower see every narration?}

I want a shared story everyone builds on.

The central thread is the party - which every player contributes to. Each player weaves their wallflower's thread around this central thread.

Each player sees their wallflower's full thread, while other players only see a quarter of each wallflower's thread. This can make for surprising reveals at the end.

It's much easier for players if every wallflower sees everything at the party. It is far too hard for players to separate out what each wallflower knows.

The narrator for each round isn't aware of which wallflower will give their impression. So every wallflower needs to be aware of what's going on.



%\pagebreak
%\section{Eratta}
%\tableofcontents

}
\end{document}